Cosmic evolution of the correlation between supermassive black hole mass and host galaxy at redshift up to 1.7

### 2019-01-21 manuscript/manuscript.tex
The update by Tommaso

Most galactic nuclei harbor a supermassive black hole (BH), whose mass (\mbh) is well known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion(\sigstar). These tight correlations indicates a connection between nuclear activity and galaxy formation and evolution \citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere and their host galaxy. On the other hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver \citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
However, for a different view, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.

One key to this study is tracing their correlation to higher redshift, determining how and when they emerged and evolved over cosmic time \citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}. During the past decade, there has been much progress on our understanding at $z<1$ using the type 1 AGN. The work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that, \mbh\ is elevated as compared to the bulge luminosity from the local relations, thus indicating that the supermassive BHs were built up first with galaxy then growing around their deep potential wells. Similarly, the works by \citet{Bennert11, Woo++08} agreed to this scenario by studying the \mbh-\smass and \mbh-\sigstar relations. Nevertheless, some studies are consistent with no evolution \citet{SS13, Sun2015, Cisternas2011}.

Despite the enormous amount of effort, there are still uncertainties stems from different aspects which could lead to the inconsistency among these works. First, the inherent uncertainties in BH mass estimates using the virial method. Especially, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-virial component of the BLR gas, when compared to local samples with masses based on broad Balmer lines \citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measurement systematics exist in the host galaxy properties. It is worth noting that strong gravitational lensing provides a unique opportunity to make progress in the study by extending the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}. Equally important, the selection effects and their impact on the observed need to be taken well into account. For instance, it has been demonstrated \citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. Even considering this selection effect, an evolution of the scaling relations is expected from simulations \citep{DeG++15} and with respect to the bulge mass.

To make progress, it is essential to make use of the larger sample to high-quality data in respect of the measurement of both the host properties and the \mbh. On the other hand, extending the correlations to higher redshift ($z>1$) would effectively improve the statistics, where the \mbh-\lhost\ is steeper than the current observational measurements at lower redshift, before self-regulation slows the black hole growth and galaxies settle onto the local mass relation \citep{DeG++15}.

In this study, we aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \citep{Aird2015}.  At this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS. Our study overcomes the biases in the following way. First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function. Second, we estimate \mbh\ using Balmer lines which avoids the systematics by \Mgii. Third, our X-ray selected sample have lower nuclear-to-host ratios which facilitate the galaxy mass measurements. Moreover, 21/32 systems of our sample have two-band \hst\ data (i.e. WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference. Given the high-quality data at such redshift, we test whether the growth of BH predates that of the host by a factor of at least $1.7$ $(\sim0.23$ dex).

@@

For the calibration with the local relation, we introduce the well-defined 19 local AGN measurements \citep{Ben++10, Peterson2004} which defines the zero-point. 
To compare with the samples in the literature, we also adopt the samples from \citet{Ding2017b}, which includes the measurements by \citet{Pen++06qsob, Park15} to study the \mbh-\lhost\ of 127 objects by \hst.

\subsection{Observation and reduction}
\label{observation}
\subsubsection{HST image Observation}
% The AGN surface photometry in IR Channel Filters.\\
The high spatial resolution of the host image is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass. All the new 32 AGN systems were observed with the HST/WFC3 infrared channel, as the HST program GO-15115, PI: John Silverman. We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets. This selection could ensure that the broad \halpha\ line ($4000\AA$) is not present in the bandpass which could contaminate the host emissions due to the broad wings of the PSF.

%Drizzling, background noise...
For the new 32 AGN systems, each target one has six separate exposures with $\sim399s$ (i.e. total exposure time $\sim2394s$). The six exposures for each dither image were combined by the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel. 
To accurately estimate the background light which could come from both the sky and the detector, we adopt the {\sc photutils} to measure the photometry.

@@

\subsubsection{AGN Emission Line}
\label{sec:bh_mass}
% The introduction of the BH inferred by the board emission line.
The \mbh\ of type-1 AGNs can be inferred using the so-called virial method \citep{Peterson2004, Shen2013}. The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity virializes the motion of the BLR gas. In this scenario, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size. As a result, the estimation of the \mbh\ is achieved by these measurements.

For our targets, the \halpha\ and \hbeta\ emission-line properties have been investigated by \citet{Schulze2018} using the multi-object spectrograph Subaru/FMOS. We referred to this paper for the details of continuum fitting and emission line modeling. Since the other compared AGNs in the literature used different calibrations of the virial method, we compare the difference among the recipes by \citet{Schulze2018, McG++08, Ding2017b} and adopt a list of consistent ones to cross-calibrate the \mbh\ for all the samples, in order to avoid any systematic bias in Section~\ref{mbh}.

@@

\subsection{Surface Photometry}
\subsubsection{PSF library}    
\label{sec:psf_library}
%Introduce the PSF library
The knowledge of the PSF is crucial for the AGN imaging decomposition, especially when the nuclear image is unresolved with light distributed as the point source. The PSF is known to be varied with different frame position and the intensity, due to the effect of aberrations. The simulated PSF, such as {\sc TinyTim} ones, are usually poor matches to observations \citet{Mechtley2012}. Empirical PSF stars are considered better than the simulated ones, since they were observed simultaneously with the science target which were reduced and analyzed in the same way \citet{Kim2008, Park15}

To minimize the impact of the mismatch, we build a PSF library by selecting the isolated, unsaturated PSF-stars with high S/N from the overall AGN field. The selection is completed by the following steps. We first adopt the identified stars as candidates from the COSMOS2015 catalog by \citet{Laigle2016}. A lot of bright stars with intensity similar to the AGNs were excluded by \citet{Laigle2016}; in the second step, we manually select the PSF-like objects as candidates. We then remove the non-ideal PSF candidates based on their intensity, FWHM, central symmetry and any that were contaminated by nearby objects. Finally, the PSF library contains 78 and 36 PSFs for F140W and F125W, respectively.

We assume that the overall PSF-stars in the library cover all possible PSF light distribution. Therefore, when fitting to data, the entire inference would bracket the true answer.
%In the next subsection, we carry out the AGN decomposition using each PSF. We rank their performance based on the goodness (i.e. $\chi^2$) so that the final inference of the host properties are weighted from the top-rank PSFs.

%\subsubsection{Surface Photometry modeling method}
\subsubsection{AGN-host Decomposition}
%Introduce the lenstronomy. Model the PSF in each library.\\
%Inspired by Simon's work, we rank the performance of the each PSF and weight for the final fitting result. 
We simultaneously fit the two-dimensional flux distribution of the center nuclear and the underlying host galaxy. As a common practice, we assume the unresolved nuclear as a scaled point source, while the host galaxy as a \sersic\ profile. Note that the actual morphologies of the host galaxies could be even more complicated (e.g. bulge+disk). However, the purpose of adopting the \sersic\ model is a simplified a first-order approximation of the surface brightness distribution with a flexible parameterization which provides sufficient freedom to infer the host flux, given the high redshift range of our sample. Furthermore, we fit the galaxies which close to the AGN as the \sersic\ model, to account for the contamination of their light.

%Introduce Lenstronomy:
We adopt the imaging modeling tool \lenstronomy\ \citep{lenstronomy} to perform the decomposition of the host and nuclear light. \lenstronomy\ is a multi-purpose open-source gravitational lens image modeling python package. 
Its flexibility enables us to turn off the lensing channel and focus on the AGN decomposition\footnote{For a sanity check, we compared the performance of \lenstronomy\ to the most commonly used galaxy modeling software {\sc Galfit} and confirm that the consistent result could be obtained with the same fitting ingredients provided.}. The input ingredients to \lenstronomy\ include:
\begin{enumerate}
\item AGN imaging data. \\
-- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ covers sufficient AGN light our samples. By default, we cut out the AGN image to a $61\times61$ pixels box (i.e. $4''\times 4''$). If needed, the larger size box would be sufficient to include the nearby objects. 
\item Noise level map.\\
-- The origin of the noise in each pixel stems from the read noise, background noise and Poisson noise by the astronomical sources themselves. To take them into account, we measure the read noise and background noise level directly from the empty regions of the data. We calculate the effective exposure time of each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level. 
\item PSF. \\
-- 
The PSF is directly taken from the PSF library. Usually, the mismatch exists when subtracting the AGN as the scaled PSF, especially at the central parts. We also note that, in the lens modeling, this mismatch can be mitigated with PSF reconstruction by the iterative method \citep{Chen2016, Birrer2018}.  However, this approach incorporates with the information of the lensing feature which is not suitable for our case. If one enforces to perform the PSF reconstruction, the iterative correction would absorb all mismatch information, result in a biased host inference. Hopefully, our library contains sufficient information to cover all the possible PSF, and the entire inference would bracket the true answer. 
\end{enumerate}

%Introduce the final inference using fitting:
The host properties of one AGN system is inferred through several steps. First, we decompose the AGN-host using each PSFs in the library. Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC. However, in our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow.}.
To avoid any unphysical inference, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{}]$, and Sersic index $n\in[1,7]$. Since the inference by each PSF could be the right answer, we save all of them as our entire inference. Then, we extract the best answer from the entire inference. We rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs. We infer the host property (i.e., host flux, \Reff, Sersic index $n$) using weighted arithmetic mean, and the weight is calculated by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is the inflation parameter so that when $i=8$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2
\end{eqnarray} 
Note that since each AGN system has different seeing condition, the top-eight PSFs are usually varies from one AGN system to another. Given the weights, the inferred value of host properties and the root-mean-square ($\sigma$) are calculated as:
\begin{eqnarray}
\label{eq:infer_value}
\bar{x}  =  \frac{  \sum_{i=1}^{8}   x_i * w_i  }{\Sigma w_i} ,
\end{eqnarray} 
\begin{eqnarray}
\sigma =   \sqrt{ \frac{  \sum_{i=1}^{8}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
\end{eqnarray}

%ECDFS-358 and CID206
In Figure~\ref{fig:AGN_decomp}, we demonstrate the optimized results inferred by \lenstronomy, including the AGN images, best-fit models, image subtract point source (i.e. host) and the residuals. As an example, the weighting values in the analysis of system COSMOS-CID1174 are listed in Table~\ref{tab:weight_CID1174}. In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index $n$ and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.

The inference of the host properties is weighted by eight top-ranked PSFs. To understand how the amount of top-ranked PSF affects our inference, we compare to the one inferred by five and ten top-ranked PSFs. As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference is solid when the amount of selected PSF exceeds five.

%The inference of F814w data.
18/32 systems in the COSMOS field have ACS/F184W imaging data. Likewise, we infer their host properties using the same approach. The field of view by ACS are larger than WFC3, and we collected in total 174 ACS PSFs in the library. In principle, the host inference by IR band is superior to the one by UV band, giving that the effects of dust extinction and contrast between the (blue) AGN and (red) host. Thus, we fix the \Reff\ and \sersic\ $n$ as the value inferred by IR band, assuming that the morphology of the galaxy is consistent between ACS and WFC3.

@@

\tablecaption{The inference of the host information by the AGN decomposition for the 32 systems.} 

@@

  \multicolumn{5}{c}{Inference by WFC3}&
  \multicolumn{3}{c}{Inference by ACS} \\

@@

\colhead{reduced $\chi ^2$}& \colhead{host flux ratio}& 

@@

\colhead{reduced $\chi ^2$}& \colhead{host flux ratio}& \colhead{magnitude} & \colhead{$\log L_R$}\\

@@

Column~3-6: Host inference by the WFC3 image.
Column~7-9: Host inference by the ACS image. 
Column~10: The inferred host Luminosity in the rest-frame R band.

@@

\begin{figure*}
\centering
{
\includegraphics[height=0.35\textwidth]{fig/hist_compare.pdf}
}
\caption{\label{fig:hist_compare} 
The comparison of the histogram of the inferred host flux ratio, based on the different amount of the top-ranked PSFs.}
\end{figure*}

>>>>

Most galactic nuclei are thought to harbor a supermassive black hole (BH), whose mass (\mbh) is well known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion(\sigstar). These tight correlations indicate a connection between nuclear activity and galaxy formation and evolution \citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere and their host galaxy. On the one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver \citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.

A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time \citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}. During the past decade, there has been much progress on this front at $z<1$ using type 1 AGNs. For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed bulge luminosity compared to the local relations. This offset is consistent with a scenario in which supermassive BHs were built up first with galaxy then growing around their deep potential wells. Similarly, the works by \citet{Bennert11, Woo++08} agreed to this scenario by studying the \mbh-\smass and \mbh-\sigstar relations. Nevertheless, the evolution is detected at low significance given the considerable error bars, and some studies report results consistent with no evolution \citet{SS13, Sun2015, Cisternas2011}.

In order to make progress it is important to reduced as much as possible the uncertainties and take great care of selection effects and systematic errors. First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called "virial" method. In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-virial component of the BLR gas, when compared to local samples with masses based on broad Balmer lines \citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging. Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed quasars, since lensing magnifies the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}. Last but not least, the selection function needs to be taken into account when intepreting the observations \citep{Treu2007,Lauer2007}. For instance, it has been demonstrated \citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. It is also important to consider the selection function when comparing the observed scaling relations with simulated ones \citep{DeG++15}.

In this study, we aim to make progress by making use of a large sample with high-quality data both for the measurement of both the host properties and the \mbh, extending to the highest redshifts where evolutionary effects should be strongest \citep{DeG++15}. In practice, we aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \citep{Aird2015}.  In this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS. Our study overcomes the biases in the following way. First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function. Second, we estimate \mbh\ using Balmer lines which avoids the systematics by \Mgii. Third, our X-ray selected sample have lower nuclear-to-host ratios which facilitate the galaxy mass measurements. Moreover, 21/32 systems in our sample have two-band \hst\ data (i.e. WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference. Given the high-quality data at such redshift, we can test whether the growth of BH predates that of the host by a factor of at least $1.7$ $(\sim0.23$ dex).

@@

For the calibration with the local relation, we use 19 local AGN measurements \citep{Ben++10, Peterson2004} which define the zero-point. 
To compare with the samples in the literature, we also adopt the samples from \citet{Ding2017b}, which include the measurements by \citet{Pen++06qsob, Park15} to study the \mbh-\lhost\ of 127 objects by \hst.

\subsection{Observation and reduction}
\label{observation}
\subsubsection{HST image Observation}
% The AGN surface photometry in IR Channel Filters.\\
The high spatial resolution of the host image is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass. All the new 32 AGN systems were observed with the HST/WFC3 infrared channel, as the HST program GO-15115, PI: John Silverman. We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets. This selection ensures that the broad \halpha\ line ($4000\AA$) is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.

%Drizzling, background noise...
For each of the 32 new AGNs we took six separate exposures with $\sim399s$ (i.e. total exposure time $\sim2394s$). The six exposures for each dither image were combined with the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel. 
To accurately estimate the background light which could come from both the sky and the detector, we adopt the {\sc photutils} to measure the photometry.

@@

\subsubsection{AGN Emission Line}
\label{sec:bh_mass}
% The introduction of the BH inferred by the board emission line.
The \mbh\ of type-1 AGNs can be inferred using the so-called virial method \citep{Peterson2004, Shen2013}. The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas. In this scenario, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size. As a result, the estimation of the \mbh\ is achieved by these measurements.

For our targets, the \halpha\ and \hbeta\ emission-line properties have been investigated by \citet{Schulze2018} using the multi-object spectrograph Subaru/FMOS. We referred to that paper for the details of continuum fitting and emission line modeling. Since the other compared AGNs in the literature used different calibrations of the virial method, we compare the difference among the recipes by \citet{Schulze2018, McG++08, Ding2017b} and adopt a list of consistent ones to cross-calibrate the \mbh\ for all the samples, in order to avoid any systematic bias in Section~\ref{mbh}.

@@

\subsection{Surface Photometry}
\subsubsection{PSF library}    
\label{sec:psf_library}
%Introduce the PSF library
The knowledge of the PSF is crucial for the AGN imaging decomposition, especially when the nuclear image is unresolved with light distributed as the point source. The PSF is known to be vary across the detector and with time, due to the effect of aberrations and breathing. Simulated PSF, such as {\sc TinyTim} ones, are usually insufficient matches to observations for our purposes \citet{Mechtley2012}. Stars within the fields provide a better description than the simulated PSF, since they were observed simultaneously with the science targets and reduced and analyzed in the same way \citet{Kim2008, Park15}

To minimize the impact of the mismatch, we build a PSF library by selecting all the isolated, unsaturated PSF-stars with high S/N from our entire program. The selection consists of the following steps. We first adopt the identified stars as candidates from the COSMOS2015 catalog by \citet{Laigle2016}. A lot of bright stars with intensity similar to the AGNs were excluded by \citet{Laigle2016}; in the second step, we manually select the PSF-like objects as candidates. We then remove the non-ideal PSF candidates based on their intensity, FWHM, central symmetry and any that were contaminated by nearby objects. In the end, the PSF library contains 78 and 36 PSFs for F140W and F125W, respectively.

We assume that the stars in the library are representative of the possible PSFs in our program. Therefore, we assume that the PSF library gives a good representation of the dominant source of uncertainty as well as the best fit.
%In the next subsection, we carry out the AGN decomposition using each PSF. We rank their performance based on the goodness (i.e. $\chi^2$) so that the final inference of the host properties are weighted from the top-rank PSFs.

%\subsubsection{Surface Photometry modeling method}
\subsubsection{AGN-host Decomposition}
%Introduce the lenstronomy. Model the PSF in each library.\\
%Inspired by Simon's work, we rank the performance of the each PSF and weight for the final fitting result. 
We simultaneously fit the two-dimensional flux distribution of the center nuclear and the underlying host galaxy. Following common practice, we assume the unresolved nuclear as a scaled point source, while the host galaxy as a \sersic\ profile. Note that the actual morphologies of the host galaxies could be more complicated (e.g. bulge+disk). However, the purpose of adopting the \sersic\ model is a simplified a first-order approximation of the surface brightness distribution with a flexible parameterization which provides sufficient freedom to infer the host flux, given the high redshift range of our sample. Furthermore, we fit other galaxies that happen to be close to the AGN as additional \sersic\ model, to account for any potential contamination.

%Introduce Lenstronomy:
We adopt the imaging modeling tool \lenstronomy\ \citep{lenstronomy} to perform the decomposition of the host and nuclear light. \lenstronomy\ is a multi-purpose open-source gravitational lens image modeling python package. 
Its flexibility enables us to turn off the lensing channel and focus on the AGN decomposition\footnote{For a sanity check, we compared the performance of \lenstronomy\ to the most commonly used galaxy modeling software {\sc Galfit} and confirm that the consistent result could be obtained with the same fitting ingredients provided.}. The maim advantage over {\sc Galfit} is that \lenstronomy returns the full posterior of the parameter and not just the best fit model and the Laplace approximation of the uncertanties. The input ingredients to \lenstronomy\ include:
\begin{enumerate}
\item AGN imaging data. \\
-- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ covers sufficient AGN light our samples. By default, we cut out the AGN image to a $61\times61$ pixels box (i.e. $4''\times 4''$). If needed, the larger size box would be sufficient to include the nearby objects. 
\item Noise level map.\\
-- The origin of the noise in each pixel stems from the read noise, background noise and Poisson noise by the astronomical sources themselves. To take them into account, we measure the read noise and background noise level directly from the empty regions of the data. We calculate the effective exposure time of each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level. 
\item PSF. \\
-- 
The PSF is directly taken from the PSF library. Usually, a mismatch exists when subtracting the AGN as the scaled PSF, especially at the central parts. While modeling multiply imaged AGN, this mismatch can be mitigated with PSF reconstruction by the iterative method \citep{Chen2016, Birrer2018}.  However, this approach requires multiple images which are not available in our case.  We remedy this deficiency by using a broad library which should contain sufficient information to cover all the possible PSF. 
\end{enumerate}

%Introduce the final inference using fitting:
The host properties of one AGN system is inferred via the following steps. First, we model the AGN and host using each PSFs in the library. Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC. However, in our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow.}.
To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{}]$, and Sersic index $n\in[1,7]$. Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs. We infer the host property (i.e., host flux, \Reff, Sersic index $n$) using a weighted arithmetic mean. The weight is calculated by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter so that when $i=8$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2,
\end{eqnarray} 
The goal of this recipe is to weight each PSF based on their relative goodness of fit, while ensuring at least eight are used to capture the range of systematic uncertainties. The answers would not change significantly if we had chosen a different number of PSFs, as we show below.

Note that since each AGN system was observed in different location of the detector and at a different time, the top-eight PSFs usually vary from one AGN system to another. Given the weights, the inferred value of host properties and the root-mean-square ($\sigma$) are calculated as:
\begin{eqnarray}
\label{eq:infer_value}
\bar{x}  =  \frac{  \sum_{i=1}^{8}   x_i * w_i  }{\Sigma w_i} ,
\end{eqnarray} 
\begin{eqnarray}
\sigma =   \sqrt{ \frac{  \sum_{i=1}^{8}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
\end{eqnarray}

%ECDFS-358 and CID206
In Figure~\ref{fig:AGN_decomp}, we demonstrate the optimized results inferred by \lenstronomy, including the AGN images, best-fit models, image subtract point source (i.e. host) and the residuals. As an example, the weights adopted in the analysis of system COSMOS-CID1174 are listed in Table~\ref{tab:weight_CID1174}. In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index $n$ and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.

The inference of the host properties is weighted by eight top-ranked PSFs. To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the one inferred by five and ten top-ranked PSFs. As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference is solid when the amount of selected PSF exceeds five. For a smaller number of PSFs one tends to underestimate the uncertainties.

%The inference of F814w data.
18/32 systems in the COSMOS field have ACS/F184W imaging data. We infer their host properties using the same approach used for the WFC3-IR data. The field of view by ACS are larger than WFC3, and we collected in total 174 ACS PSFs in the library. In principle, the host inference by IR band is superior to the one by UV band, giving that the effects of dust extinction and contrast between the (blue) AGN and (red) host. Thus, we fix the \Reff\ and \sersic\ $n$ as the value inferred by IR band, assuming that the morphology of the galaxy is consistent between ACS and WFC3.

@@

\tablecaption{Inferred host galaxy parameters for the 32 systems.} 

@@

  \multicolumn{5}{c}{WFC3}&
  \multicolumn{3}{c}{ACS} \\

@@

\colhead{reduced $\chi ^2$}& \colhead{host-to-total flux ratio}& 

@@

\colhead{reduced $\chi ^2$}& \colhead{host-to-total flux ratio}& \colhead{magnitude} & \colhead{$\log L_R$}\\

@@

Column~3-6: WFC3 inference.
Column~7-9: ACS inference. 
Column~10: Inferred host Luminosity in the rest-frame R band.

@@

\begin{figure*}
\centering
{
\includegraphics[height=0.35\textwidth]{fig/hist_compare.pdf}
}
\caption{\label{fig:hist_compare} 
Comparison of the histogram of the inferred host flux ratio, based on the different amount of the top-ranked PSFs.}
\end{figure*}
